### 2016-07-26 notions.tex
restructuring
cheers

\section{Security Notions}
\tsnote{intro text}

\subsection{Correctness Against Adaptive Adversaries}
As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
we are interested in defining an adaptive (i.e., adversarial) notion
of correctness.   Figure~\ref{fig:correctness} describes a security
experiment that captures such a notion.

>>>>

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
we are interested in defining an adaptive (i.e., adversarial) notion
of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
that captures such a notion.

In addition to correctness, we establish notions of privacy for set-representations.  We explore two notions.  The first has the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size), and is given $(M,\aux)$ where~$M$ represents $S_b$ for a uniform bit~$b$.  In this game, the adversary must determine which set~$M$ represents.

\subsection{Correctness Against Adaptive Adversaries}
